A Classical Density-Functional Theory for Describing Water Interfaces

### 2013-05-08 papers/water-saft/paper.tex
add paper for new water functional (not yet modified from old one) Tested everything on bennet.

\author{Jessica Hughes}
\affiliation{Department of Physics, Oregon State University,
  Corvallis, OR 97331, USA}
\author{Eric J. Krebs}
\affiliation{Department of Physics, Oregon State University,
  Corvallis, OR 97331, USA}
\author{David Roundy}
\affiliation{Department of Physics, Oregon State University,
  Corvallis, OR 97331, USA}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We develop a classical density functional for water which combines the
White Bear fundamental-measure theory (FMT) functional for the hard
sphere fluid with attractive interactions based on the Statistical
Associating Fluid Theory (SAFT-VR).  This functional reproduces the
properties of water at both long and short length scales over a wide
range of temperatures, and is computationally efficient, comparable to
the cost of FMT itself.  We demonstrate our functional by applying it
to systems composed of two hard rods, four hard rods arranged in a
square and hard spheres in water.
\end{abstract}
\maketitle

>>>>

\author{Eric J. Krebs}
\affiliation{Department of Physics, Oregon State University,
  Corvallis, OR 97331, USA}
\author{Jeff B. Schulte}
\affiliation{Department of Physics, Oregon State University,
  Corvallis, OR 97331, USA}
\author{David Roundy}
\affiliation{Department of Physics, Oregon State University,
  Corvallis, OR 97331, USA}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We develop an improved version of our old functional.
\end{abstract}
\maketitle
